---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.path = "NEWS-")
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# Version History

## Changes in Version 0.1.0.9004 (2022-01-25)

* feature: Add Shiny app
* docs: Update DESCRIPTION with package for Shiny app
* docs: Add data-raw folder for generating HTML text for Shiny app

## Changes in Version 0.1.0.9003 (2022-01-25)

* style: Trim lines to 80 characters
    + runShiny.R
* style: Fix spelling
    + README

## Changes in Version 0.1.0.9002 (2022-01-21)

* doc: Add GitHub Actions with usethis package
    + check standard
    + codecov
    + test-coverage
    + pkgdown

## Changes in Version 0.1.0.9001 (2022-01-21)

* feature: Update package with basics
    + DESCRIPTION
    + NEWS
    + README
    + Library Creation helper RMD
    + Shiny folder
    + runShiny function

## Changes in Version 0.1.0 (2022-01-21)

* feature: Initial commit on GitHub

    
