---
title: "R Notebook"
subtitle: "Parent with Children"
output: html_notebook
---

# Purpose

Test out parent-child chunk set up in R Notebook.

https://bookdown.org/yihui/rmarkdown-cookbook/child-document.html

# Main
Loop through a few options and have them as Child chunks.

Use mtcars dataset

```{r start}
knitr::kable(head(mtcars), caption = "mtcars (head).")

#cat(summary(mtcars))

param_user <- c("Mazda RX4", "Honda Civic", "Camaro Z28", "Ford Mustang")
param_children <- param_user[param_user %in% rownames(mtcars)]
param_children_len <- length(param_children)

```

## Child Docs
Use separate Child docs (that are the same) and number them.
Then include or not based on number of parameters.



```{r comment}
# ```{r child01, echo=TRUE, results='asis', child=if(param_children_len >= 1) 'Test_Parent_Child_01.Rmd'}
# param_num <- 1
# cat(paste0("## Child", param_num, "a"))
# ```
# 
# ```{r child02, echo=FALSE, results='asis', child=if(param_children_len >= 2) 'Test_Parent_Child_01.Rmd'}
# param_num <- 2
# cat(paste0("## Child", param_num, "a"))
# ```
```

https://bookdown.org/yihui/rmarkdown-cookbook/child-document.html

```{r, echo=FALSE, results='asis'}
res <- lapply(setdiff(names(mtcars), 'mpg'), function(x) {
  knitr::knit_child('Test_Parent_Child_01.Rmd'
                    , envir = environment()
                    , quiet = TRUE)
})
cat(unlist(res), sep = '\n')
```
